---
title: "Assignment 1"
author: "Your Name"
date: "Sepemmber 13, 2023"
format:
  html:
    toc: true
    number-sections: true
    colorlinks: true
    smooth-scroll: true
    embed-resources: true

author_profile: yes
permalink: /teaching/
---

# Instructions {-}

Please submit your assignment as html file to me via email. Please call your assignment: "yourname_assignment1.html". For example, I would submit submit something called "popescu_assignment1.html". Please make sure that it is all in lower case. Please answer all the questions below

# Question

Remove the word "mouse" from the following vector and create a new object
```{r}
list_animals <- c("mouse", "rat", "dog", "cat")
```


# Question

Remove from the following list all the numbers between 30 and 60 (inclusive)
```{r}
list_no<-c(10, 20, 30, 40, 50, 60, 70)
```


# Question

Remove the following elements using the %in% operator from the list:
tigers, elephants, giraffes, monkeys
```{r}
big_list_animals<-c("cheetah", "tigers", "gorillas", "dolphins", "elephants", "giraffes", "monkeys")
```

# Question

Explain in your words: Why does the following return "four" > "five" return TRUE
```{r}
"two" > "ten"
```

# Question

Remove the missing data from the following list
```{r}
list_animals <- c("mouse", "rat", NA, "dog", "cat")

```

# Question

Calculate the mean from the following list of numbers
```{r}
list_no<-c(1, 2, 3, 4, 5, 6, 7, 8, 9, NA, 10, 11, NA)
```

# Question

Calculate the median from the following list of numbers
```{r}
list_no<-c(1, 2, 3, 4, 5, 6, 7, 8, 9, NA, 10, 11, NA)
```

# Question

Open the life expectancy database
```{r}
setwd("/Users/bgpopescu/Dropbox/john_cabot/teaching/stats/assignment1/")
life_expectancy <- read.csv(file = './life-expectancy.csv')
```


# Question

Select Italy after 2000 (inclusice)
```{r}
```

# Question

Select US after 2000
```{r}
```

# Question

What is the average life expectancy for Italy after 2000 (inclusive)?
```{r}
```

# Question

What is the average life expectancy for the US after 2000 (inclusive)?
```{r}
```

# Question

What is the median life expectancy for Italy and the US after 2000 (inclusive)?
```{r}
```

# Question

What is the standard deviation life expectancy for Italy and the US after 2000 (inclusive)?
```{r}
```

# Question

What is the highest life expectancy in the entire world?

```{r}
```

# Question

What is the lowest life expectancy in the entire world?

```{r}
```

# Question

What is the name of the country with the highest life expectancy for the entire dataset and all years?

```{r}
```

# Question

What are the years for that country with the highest life expectancy for the entire dataset and all years?

```{r}
```

# Question

What is the name of the country with the lowest life expectancy for the entire dataset and all years?
```{r}
```

# Question

What are the years for that country with the lowest life expectancy for the entire dataset and all years?
```{r}
```




