---
title: "Assignment 2: Exercise 2"
author:
  name: Bogdan G. Popescu
  email: bogdan.popescu@johncabot.edu
  affiliations: John Cabot University
format:
  revealjs:
    smooth-scroll: true
    slide-number: c/t
    show-slide-number: all
    preview-links: auto
    width: 1050
    height: 700
    fontsize: 24pt
    footer: "Popescu (JCU): Lecture 9"
    sansfont: Latin Modern Roman
    embed-resources: true
    includes:
---


# Question 

Suppose you have two datasets:

::: fragment
Dataset1:
```{r, echo=TRUE, eval=TRUE}
# Sample data for employee_data
employee_data <- data.frame(
  employee_id = c(101, 102, 103, 104, 105),
  name = c("Alice", "Bob", "Charlie", "David", "Eve"),
  department = c("HR", "Finance", "Marketing", "IT", "Operations")
)
```
:::

::: fragment
Dataset2:
```{r, echo=TRUE, eval=TRUE}
# Sample data for performance_data
performance_data <- data.frame(
  employee_id = c(101, 102, 103, 104, 105),
  rating = c(4.5, 3.2, 2.9, 4.8, 3.7),
  bonus = c(1000, 800, 500, 1200, 900)
)
```
:::

# Instructions

::: fragment
Create a function `employee_performance_analysis` that takes the two datasets as inputs and performs the following tasks:
:::

::: fragment
Step1: Merge `employee_data` with `performance_data` based on the `employee_id.`
:::

::: fragment
Step2: Calculate a new column `performance_grade` based on the following criteria:

  - If `rating` is greater than or equal to 4, assign "High".
  - If `rating` is between 3 and 4, assign "Medium".
  - If `rating` is less than 3, assign "Low".
:::

::: fragment
Step3: Return the merged dataset with the added `performance_grade` column.  
:::

# The Approach

```{r, echo=TRUE, eval=TRUE, warning=FALSE, message=FALSE}
#| code-line-numbers: "1-2|3-4|5-6|7-9|10-12"
#Loading the library
library(dplyr)
# Define function employee_performance_analysis
employee_performance_analysis <- function(df1, df2) {
  #Step 1: Merge df1 with df2
  merged_df <- left_join(df1, df2, by = "employee_id")
  #Step 2: Calculate performance_grade based on rating
  merged_df$performance_grade <- ifelse(merged_df$rating >= 4, "High",
                                          ifelse(merged_df$rating >= 3, "Medium", "Low"))
  #Returning the df
  return(merged_df)
}
```
  
# Testing the Function

```{r, echo=TRUE, eval=TRUE}
# Test the function
employee_performance <- employee_performance_analysis(employee_data, performance_data)
employee_performance
```
